### 2022-10-14 manuscript.Rmd
add my affilitation
rename bibfile (spaces in filename)
add repro

author: 
  - name          : "Elisa S. Buchberger"
    affiliation   : "1"
    corresponding : yes
    address       : "Lentzeallee 94, 14195 Berlin"
    email         : "buchberger@mpib-berlin.mpg.de"
  - name          : "Chi T. Ngo"
    affiliation   : "1"
  - name          : "Aaron Peikert"
    affiliation   : "1"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
  - name          : "Markus Werkle-Bergner"
    affiliation   : "1"

@@

bibliography      : "Power Simulation Manuscript.bib"

@@

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

builtin_source_hook <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  x <- grep("# HIDE$", x, invert = TRUE, value = TRUE)
  if (length(x) > 0) {
    return(builtin_source_hook(x, options))
  } else {
    invisible(NULL)
  }
})
```

>>>>

author: 
  - name          : "Elisa S. Buchberger"
    affiliation   : "1"
    corresponding : yes
    address       : "Lentzeallee 94, 14195 Berlin"
    email         : "buchberger@mpib-berlin.mpg.de"
  - name          : "Chi T. Ngo"
    affiliation   : "1"
  - name          : "Aaron Peikert"
    affiliation   : "1, 2"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
  - name          : "Markus Werkle-Bergner"
    affiliation   : "1"

@@

bibliography      : "references.bib"

@@

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - "01_run_simulation.R"
---

@@

builtin_source_hook <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  #raw <- x
  #browser()
  x <- unlist(stringr::str_split(x, "\n"))
  ind <- stringr::str_which(x, "# HIDE$")
  if(length(ind) > 1){
    first <- ind[1]
    rest <- ind[-1]
    x[first] <- "# […]"
    x <- x[-rest]
  } else if(length(ind) == 1L){
    x[ind] <- "# […]"
  }
  first <- ind
  if (length(x) > 0) {
    return(builtin_source_hook(x, options))
  } else {
    invisible(NULL)
  }
})
```
